Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-23 main_paper.tex
Relabel equations and assumptions
Small internal change to the source code: this commit changes the
'labels' used for internal references to be sequential.

\begin{assumption}[Bandwidth]\label{A3}
  Let $h_n$ be the bandwidth used to estimate the local polynomial of
  order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then
  $h_n = o(n^{-1/5})$, $b_n = o(n^{-1/5})$, $n h_n \to \infty$, and
  $n b_n \to \infty$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to
    hold as $n \to \infty$.} %
  The relationship $h_n \leq b_n$ also holds for all $n$.
\end{assumption}

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A3} and
  define
  \begin{align}
    I^-(h) &= \{i : h < X_i < 0\}, &
    I^+(h) &= \{i : 0 < X_i < h\}.
  \end{align}
  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
  $I^-(h_n)$ and $I^+(h_n)$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:4}
      \Delta^* = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
    \end{equation}
  \end{enumerate}
\end{algorithm}
Obviously, the distribution of $\Delta^*$ depends on $B_1$ and we could
incorporate that dependency into our notation by wrting
$\Delta^*_{B_1}$. However, we will follow standard practice in the bootstrap
literature and assume that $B_1$ is large enough that it can be ignored and
define $\Delta^* = \plim_{B_1 \to \infty} \Delta^*_{B_1}$

@@

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A3},
  $(\hat\tau(h_n,b_n) - \Delta^*(h_n,b_n) - \tau) / V^{1/2}(h_n, b_n) \to^d N(0,1)$.
\end{theorem}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define $I^-$, $I^+$, $M^-$, and $M^+$ as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:6}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_2$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_B^{\prime*}$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{equation*}
        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M^-(b_n)}^{*-},X_{M^-(b_n)}^{*-}),
        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M^+(b_n)}^{*+},X_{M^+(b_n)}^{*+}),
      \end{equation*}
      using the same bandwidths $h_n$ and $b_n$ that are used in the rest of
      this algorithm but reestimating all of the local polynomials on the
      bootstrap data. Let $\Delta^{**}$ represent the bias estimator returned
      by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*} = \hat\mu_+^* - \hat\mu_i^* - \Delta^{**}$.
    \end{enumerate}
  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
  \end{enumerate}
\end{algorithm}

@@

\begin{lemma}\label{L2}
  Under Assumptions~\ref{A1} and~\ref{A3},
  $\Delta^{**} = \E^* \hat\tau^* - \tau^* + o_{p^*}(-)$.
\end{lemma}

\begin{theorem}\label{T2}
  Let $\Pr_\tau$ represent the probability distribution of the random variables
  under the assumption that $\tau$ is the true value of the ATE and suppose
  Assumptions~\ref{A1} and~\ref{A3} hold. Then
  \begin{equation}
    \label{eq:5}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau \leq \hat u(\alpha)] \geq 1 - \alpha.
  \end{equation}
  Both of the one-sided intervals are asymptotically valid under the same
  assumptions as well:
  \begin{align}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau ] &\geq 1 - \alpha / 2, &
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\tau \leq \hat u(\alpha)] &\geq 1 - \alpha / 2.
  \end{align}
\end{theorem}

@@

The design of the bootstrap ensures that
\begin{equation*}
  \label{eq:7}
  \E^* \hat\mu_{\pm}^*(h) - \mu_{\pm}^{*} = h^{2} \mu_\pm^{*(2)} \Bf_{\pm}(h)/2,
\end{equation*}
almost surely, implying that
\begin{equation*}
  \label{eq:20}
    \E^* \hat\tau^{*} - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align*}
  \hat\tau &- \E \hat\tau + (\E \hat\tau - \tau) - (\E^* \hat\tau^* - \tau^*)\\
  &= \hat\tau - \E\hat\tau
   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
  &= \hat\tau - \E\hat\tau
   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2
   - h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})
\end{align*}
The second equality holds because
$\mu_\pm^{*(2)} = \hat\mu_{\pm}^{(2)}(b_n)$ a.s. Asymptotic normality then
follows from normality of $\hat\tau - \E\hat\tau$ and
$\hat\mu_\pm^{(2)}(b_n) - \mu_\pm^{(2)}$ using
similar arguments to CCT's Lemma SA4.D.\qed

>>>>

\begin{assumption}[Bandwidth]\label{A2}
  Let $h_n$ be the bandwidth used to estimate the local polynomial of
  order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then
  $h_n = o(n^{-1/5})$, $b_n = o(n^{-1/5})$, $n h_n \to \infty$, and
  $n b_n \to \infty$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to
    hold as $n \to \infty$.} %
  The relationship $h_n \leq b_n$ also holds for all $n$.
\end{assumption}

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A2} and
  define
  \begin{align}
    I^-(h) &= \{i : h < X_i < 0\}, &
    I^+(h) &= \{i : 0 < X_i < h\}.
  \end{align}
  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
  $I^-(h_n)$ and $I^+(h_n)$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:2}
      \Delta^* = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
    \end{equation}
  \end{enumerate}
\end{algorithm}
Obviously, the distribution of $\Delta^*$ depends on $B_1$ and we could
incorporate that dependency into our notation by wrting
$\Delta^*_{B_1}$. However, we will follow standard practice in the bootstrap
literature and assume that $B_1$ is large enough that it can be ignored and
define $\Delta^* = \plim_{B_1 \to \infty} \Delta^*_{B_1}$

@@

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
  $(\hat\tau(h_n,b_n) - \Delta^*(h_n,b_n) - \tau) / V^{1/2}(h_n, b_n) \to^d N(0,1)$.
\end{theorem}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define $I^-$, $I^+$, $M^-$, and $M^+$ as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:3}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_2$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_B^{\prime*}$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{equation*}
        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M^-(b_n)}^{*-},X_{M^-(b_n)}^{*-}),
        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M^+(b_n)}^{*+},X_{M^+(b_n)}^{*+}),
      \end{equation*}
      using the same bandwidths $h_n$ and $b_n$ that are used in the rest of
      this algorithm but reestimating all of the local polynomials on the
      bootstrap data. Let $\Delta^{**}$ represent the bias estimator returned
      by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*} = \hat\mu_+^* - \hat\mu_i^* - \Delta^{**}$.
    \end{enumerate}
  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
  \end{enumerate}
\end{algorithm}

@@

\begin{lemma}\label{L2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  $\Delta^{**} = \E^* \hat\tau^* - \tau^* + o_{p^*}(-)$.
\end{lemma}

\begin{theorem}\label{T2}
  Let $\Pr_\tau$ represent the probability distribution of the random variables
  under the assumption that $\tau$ is the true value of the ATE and suppose
  Assumptions~\ref{A1} and~\ref{A2} hold. Then
  \begin{equation}
    \label{eq:4}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau \leq \hat u(\alpha)] \geq 1 - \alpha.
  \end{equation}
  Both of the one-sided intervals are asymptotically valid under the same
  assumptions as well:
  \begin{align}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau ] &\geq 1 - \alpha / 2, &
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\tau \leq \hat u(\alpha)] &\geq 1 - \alpha / 2.
  \end{align}
\end{theorem}

@@

The design of the bootstrap ensures that
\begin{equation*}
  \label{eq:5}
  \E^* \hat\mu_{\pm}^*(h) - \mu_{\pm}^{*} = h^{2} \mu_\pm^{*(2)} \Bf_{\pm}(h)/2,
\end{equation*}
almost surely, implying that
\begin{equation*}
  \label{eq:6}
    \E^* \hat\tau^{*} - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align*}
  \hat\tau &- \E \hat\tau + (\E \hat\tau - \tau) - (\E^* \hat\tau^* - \tau^*)\\
  &= \hat\tau - \E\hat\tau
   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
  &= \hat\tau - \E\hat\tau
   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2
   - h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})
\end{align*}
The second equality holds because
$\mu_\pm^{*(2)} = \hat\mu_{\pm}^{(2)}(b_n)$ a.s. Asymptotic normality then
follows from normality of $\hat\tau - \E\hat\tau$ and
$\hat\mu_\pm^{(2)}(b_n) - \mu_\pm^{(2)}$ using
similar arguments to CCT's Lemma SA4.D.\qed
